More than one Author with different Affiliations

### 2012-06-03 paper/ms.tex
Small amounts of work

\documentclass[letterpaper, 11pt]{article}
\usepackage{authblk}	% For nice author-affil lists
\usepackage{graphicx}	% For figures
\usepackage{natbib}	% For citet and citep
\usepackage{amsmath}	% for \iint
\usepackage{bbm}	% for blackboard bold numbers
\usepackage[left=3cm,top=3cm,right=3cm]{geometry}

@@

\renewcommand{\topfraction}{0.85} \renewcommand{\textfraction}{0.1} 
\parindent=0cm

\title{Probabilistic Catalogues from Crowded Star Fields}
\author[1,2]{Brendon J. Brewer}
\author[3]{David W. Hogg}
\author[3]{Daniel Foreman-Mackey}
\affil[1]{\small Dept. of Physics, University of California, Santa Barbara, CA 93106, USA}
\affil[2]{Department of Statistics, University of Auckland, Private Bag 92019, Auckland, New Zealand
}
\affil[3]{Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Place, New York, NY, 10003, USA
}

\date{{\bf Title and author order subject to change} \\
{\bf Also nag me if you prefer American English}}

@@

\section{The Unknown Parameters}
There are $N$ stars in the field, where $N$ is unknown. Each star has an unknown
position $(x,y)$ in the plane of the sky, and an unknown flux $f$. We also
parameterise the {\it distribution} of positions by parameters $\alpha$,
and we parameterise the distribution of fluxes (aka the {\it luminosity
function}) by parameters $\beta$. In summary, the unknown parameters are:
\begin{eqnarray}
\theta = \left\{N, \alpha, \beta, \left\{x_i, y_i\right\}_{i=1}^N, 
\left\{f_i\right\}_{i=1}^N\right\}
\end{eqnarray}

The prior probability distribution for the unknown parameters can be factorised
using the product rule. With a variety of independence assumptions, the prior
can be written as:
\begin{eqnarray}
p(\theta) = p(N)p(\alpha)p(\beta)\prod_{i=1}^N p(x_i, y_i | \alpha)
p(f_i | \beta) 
\end{eqnarray}

Here, we have assumed that the luminosity function does not depend on position.
We have also assumed independence of $N$, $\alpha$ and $\beta$, which means that
learning the value of one would not tell us anything about the values of the
others. Finally, the positions and fluxes of the stars come independently from
a common distribution. If we knew the spatial distribution and the luminosity
function of the stars, then the location and flux of a particular star would not
tell us anything about the location and flux of another star.

\citep{massinf}

\section{Particular Models}
A model for the spatial distribution corresponds to a choice of functional forms
for the distributions $p(x_i, y_i | \alpha)$ and $p(f_i | \beta)$.

@@

\appendix
\section{Pixel Convolved PSF}
Consider a ``true image'' $f_0(x, y)$ with infinite resolution. We now model how
this image gives rise to the observed data. First, it is convolved with a
PSF $g(\delta_x, \delta_y)$ (assumed normalised to 1) to give the blurred image:
\begin{eqnarray}
f_{\rm{blurred}}(x, y) &=& \iint f_0(x-\delta_x, y-\delta_y)
g(\delta_x, \delta_y) \, d\delta_x \, d\delta_y \label{blur}
\end{eqnarray}
Then, we observe the blurred image with a certain pixellation. Consider a pixel.
The true flux $F$ within the pixel is:
\begin{eqnarray}
F &=& \iint_{\rm pixel} f_{\rm blurred}(x, y) \,dx'\,dy'\\
&=& \iint f_{\rm blurred}(x, y)\mathbbm{1}\left[(x,y) \in \textnormal{pixel}
\right] \,dx\,dy \label{pixel}
\end{eqnarray}
Now consider $F$ as a function of the central location $(x_c, y_c)$ of the
pixel.

@@

\subsection{Improving the Efficiency of Reversible Jump}
Instead of parameterising by $N$ and the positions and fluxes, what if we have
$3N_{\rm max}$ latent variables $\theta$ that always exist, and transform these
into
positions and fluxes by a transformation $f$:
\begin{eqnarray}
\{\mathbf{x}, \mathbf{y}, \mathbf{f}\} &=& f(\theta)
\end{eqnarray}
The transformation can be parameterised by various parameters of its own, such
that a known fraction of the fluxes end up being nonzero, etc. This could have
various advantages, most notably: when new stars are added, they are added with
low fluxes. It also turns the variable dimension problem into a fixed dimension
one, so emcee, MultiNest or similar will now work, although the multimodality problem will
still exist.

>>>>

\documentclass[letterpaper, 11pt]{article}
\usepackage{graphicx}	% For figures
\usepackage{natbib}	% For citet and citep
\usepackage{amsmath}	% for \iint
\usepackage{bbm}	% for blackboard bold numbers
\usepackage[left=3cm,top=3cm,right=3cm]{geometry}

@@

\renewcommand{\topfraction}{0.85} \renewcommand{\textfraction}{0.1} 
\parindent=0cm
\newcommand{\sparse}{\texttt{Sparse}}
\newcommand{\cluster}{\texttt{Cluster}}
\newcommand{\crowded}{\texttt{Crowded}}

\title{Probabilistic Catalogs from Crowded Star Fields}
\author{Brendon J. Brewer$^{1, 2}$, David W. Hogg$^{3}$,
and Daniel Foreman-Mackey$^{3}$ \\
\\
\small
$^1$ Department of Physics, University of California, Santa Barbara,\\
\small
CA 93106, USA \\
\small
$^2$ Department of Statistics, University of Auckland,\\
\small
Private Bag 92019, Auckland, New Zealand \\
\small
$^3$ Center for Cosmology and Particle Physics, Department of Physics,
New York University,\\
\small
4 Washington Place, New York, NY, 10003, USA
}

@@

\section{Probabilistic Catalogs}

\section{The Unknown Parameters}
There are $N$ stars in the field, where $N$ is unknown. Each star has an unknown
position $(x,y)$ in the plane of the sky, and an unknown flux $f$. We also
parameterize the {\it spatial distribution} of the stars by parameters
$\alpha$, and the distribution of fluxes (commonly known as the {\it luminosity
function}) by parameters $\beta$. In summary, the unknown parameters are:
\begin{eqnarray}
\theta = \left\{N, \alpha, \beta, \left\{x_i, y_i\right\}_{i=1}^N, 
\left\{f_i\right\}_{i=1}^N\right\}
\end{eqnarray}
The prior probability distribution for the unknown parameters can be factorized
using the product rule. With a variety of independence assumptions, the prior
can be written as:
\begin{eqnarray}
p(\theta) = p(N)p(\alpha)p(\beta)\prod_{i=1}^N p(x_i, y_i | \alpha)
p(f_i | \beta) 
\end{eqnarray}
Here, we have assumed that the luminosity function does not depend on position.
We have also assumed independence of $N$, $\alpha$ and $\beta$, which means that
learning the value of one would not tell us anything about the values of the
others. Finally, the positions and fluxes of the stars come independently from
a common distribution. If we knew the spatial distribution and the luminosity
function of the stars, then the location and flux of a particular star would
not tell us anything about the location and flux of another star.

\section{Specific Models}
A model for the spatial distribution corresponds to a choice of functional
forms for the distributions $p(x_i, y_i | \alpha)$ and $p(f_i | \beta)$.
In this paper we discuss three test cases, named \sparse, \cluster
and \crowded. For the generation of the simulated
images, we used the following assumptions:

\begin{table}
\begin{center}
\begin{tabular}{ccccc}
Test Case & Parameter & Value \\
\hline
\sparse \\
\cluster \\
\crowded
\end{tabular}
\end{center}
\end{table}

@@

\appendix
\section{Pixel Convolved PSF}
Consider a ``true image'' $f_0(x, y)$ with infinite resolution. We now model how
this image gives rise to the observed data. First, it is convolved with a
PSF $g(\delta_x, \delta_y)$ (assumed normalized to 1) to give the blurred image:
\begin{eqnarray}
f_{\rm{blurred}}(x, y) &=& \iint f_0(x-\delta_x, y-\delta_y)
g(\delta_x, \delta_y) \, d\delta_x \, d\delta_y \label{blur}
\end{eqnarray}
Then, we observe the blurred image with a certain pixellation. Consider a pixel.
The true flux $F$ within the pixel is:
\begin{eqnarray}
F &=& \iint_{\rm pixel} f_{\rm blurred}(x, y) \,dx'\,dy'\\
&=& \iint f_{\rm blurred}(x, y)\mathbbm{1}\left[(x,y) \in \textnormal{pixel}
\right] \,dx\,dy \label{pixel}
\end{eqnarray}
Now consider $F$ as a function of the central location $(x_c, y_c)$ of the
pixel.

@@

\subsection{Improving the Efficiency of Reversible Jump}
Instead of parameterising by $N$ and the positions and fluxes, what if we have
$3N_{\rm max}$ latent variables $\theta$ that always exist, and transform these
into
positions and fluxes by a transformation $f$:
\begin{eqnarray}
\{\mathbf{x}, \mathbf{y}, \mathbf{f}\} &=& f(\theta)
\end{eqnarray}
The transformation can be parameterized by various parameters of its own, such
that a known fraction of the fluxes end up being nonzero, etc. This could have
various advantages, most notably: when new stars are added, they are added with
low fluxes. It also turns the variable dimension problem into a fixed dimension
one, so emcee, MultiNest or similar will now work, although the multimodality problem will
still exist.
